---
title: "5205 Project_data analysis"
author: "Xinyun Li"
date: "11/30/2021"
output: html_document
---

```{r }
setwd("~/Downloads")
getwd()
```


### Loading data
```{r}

library(tidyverse)
data_ks <- read_csv(file="/Users/lixinyun/Downloads/kc_house_data.csv",)
head(data_ks)
dim(data_ks)
names(data_ks)
```


###  Data Cleaning: I delete the variable id and date of the data because id is not a variable we should consider to include in our linear model and date is hard to anlyse in GLM. I also deleted zipcode because there are too many zipcodes variation here so that it is hard to convert them into a categorical variable representing different areas in King city of Seattle. I changed year_renovated into a dummy variable representing whether the house was renovated or not because there are too many 0 in the original variable and i do not think that year of renovation will effect the pricing given a lot of 0 inside it. And I decompose the date into year of sale and month of sale for easier linear regression model and I also add one variable that representing the age of the house by substracting year sale by yaer built. 
```{R}
data_ks$yr_renovated <- as.integer(data_ks$yr_renovated!=0)

data_ks <- data_ks%>%mutate(yr_sale = as.double(format(date,format = "%Y")),
                            mon_sale = as.factor(format(date,format = "%m")),
                            age = yr_sale-yr_built)%>%
  rename("renovated" ="yr_renovated")%>%
  dplyr::select(-c(id,date,zipcode,yr_built))
```


#Split variable into continous and catigorical variable
```{R}
data_ks_cont <- dplyr::select(data_ks,c(price,sqft_living,sqft_lot,sqft_above,lat,long,sqft_living15,sqft_basement,sqft_lot15,age))
data_ks_cat <- dplyr::select(data_ks,-c(price,sqft_living,sqft_lot,sqft_above,lat,long,sqft_living15,sqft_basement,sqft_lot15,age))
head(data_ks_cont)
head(data_ks_cat)
```



### Detection for multicollinearity in continous variables.
```{R}
cor_cont <- cor(data_ks_cont)
library(corrplot)
corrplot(cor_cont,method = "pie")
# Delete sqft_living15,sqft_lot15,sqft_above
data_ks_cont <- dplyr::select(data_ks_cont,-c(sqft_living15,sqft_lot15,sqft_above)) 
head(data_ks_cont)
cor_cont2 <- cor(data_ks_cont)
corrplot(cor_cont2,method = "pie")
``` 

### Anova test for categorical variables: We can see that every categorical variable is significant
```{R}
data_ks_cat <- lapply(data_ks_cat, factor)
sapply(data_ks_cat, class)
model_cat <- lm(data_ks$price~.,data_ks_cat)
anova(model_cat)

```
### Checking for outliers.
```{R}
data_ks1 <- cbind(data_ks_cont,data_ks_cat)

model1 <- lm(price~., data = data_ks)
ols_plot_cooksd_bar(model1)
```
### Check for assumptions
```{R}
modelf <- lm(price~., data = data_ks)
summary(modelf)
par(mfrow = c(2, 2))
plot(modelf)

```
### Box-cox transformation vs Log transformation
```{R}
library(MASS)
bc <- boxcox(modelf)
(lambda <- bc$x[which.max(bc$y)])
box_model <- lm(((price^lambda-1)/lambda) ~ ., data = data_ks)
par(mfrow = c(2, 2))
plot(box_model)
log_model <- lm(log(price) ~ ., data = data_ks)
par(mfrow = c(2, 2))
plot(log_model)
```
### Performing weighted least square to obtain constant variance
```{R}
#perform Breusch-Pagan test
library(lmtest)
bptest(box_model)

wt <- 1 / lm(abs(box_model$residuals) ~ box_model$fitted.values)$fitted.values^2
wls_model <- lm( ((price^lambda-1)/lambda)~ ., data = data_ks, weights=wt)
par(mfrow = c(2, 2))
plot(wls_model)

library(lmtest)
bptest(wls_model)

```




```{R}

library(olsrr)
step_forward <- ols_step_forward_p(wls_model, details = TRUE)
step_forward
plot(step_forward)


```




